Joe Biden Predicted to Win 55.9% of the Popular Vote in the 2024 U.S. Presidential Election

### 2024-03-16 paper/paper.qmd
updated paper added weaknesses and limitations

library(tidyverse)
library(janitor)
library(rstanarm)
library(readr)
library(ggplot2)
library(knitr)
library(arrow)
library(kableExtra)
library(modelsummary)
library(MASS)

@@

# Model {#sec-model}
We will use multilevel regression with post-stratification (MRP) for our analysis.

## Model set-up
To predict whether a person will vote for Joe Biden or Donald Trump, we fitted a logistic regression model using data from the America's Political Pulse Survey [@americaspoliticalpulse] and post-stratified it using ACS census data [@citeIPUMS]. Logistic regression only works for binary classification, therefore we created a `vote_biden` variable during our data cleaning process, which is equal to 1 if a person's preferred candidate is Joe Biden, and 0 if it is Donald Trump.

@@

We run our model in R [@citeR] using the `stan_glm()` function of the `rstanarm` package [@rstanarm]. We use the default priors from `rstanarm`.

We use the `predict()` function in R [@citeR] to apply our logistic regression model to the ACS Census data [@citeIPUMS].

@@

Concerns about our model are discussed in more detail in this section:

@@

library(arrow)
library(broom.mixed)
library(gutenbergr)
library(haven)
library(knitr)
library(labelled)
library(modelsummary)
library(rstanarm)
library(tidybayes)
library(tidyverse)

popular vote

@@

Weaknesses and next steps should also be included.

@@

## Additional data details

@@

@@

@@

@@

## Correlation Map

@@

## Diagnostics

@@

>>>>

library(tidyverse)
library(janitor)
library(rstanarm)
library(readr)
library(ggplot2)
library(knitr)
library(arrow)
library(kableExtra)
library(modelsummary)
library(MASS)
library(broom.mixed)
library(gutenbergr)
library(haven)
library(labelled)
library(tidybayes)
library(tidyverse)

@@

# Model {#sec-model}

We will use multilevel regression with post-stratification (MRP) for our analysis.

## Model set-up

To predict whether a person will vote for Joe Biden or Donald Trump, we fitted a logistic regression model using data from the America's Political Pulse Survey [@americaspoliticalpulse] and post-stratified it using ACS census data [@citeIPUMS]. Logistic regression only works for binary classification, therefore we created a `vote_biden` variable during our data cleaning process, which is equal to 1 if a person's preferred candidate is Joe Biden, and 0 if it is Donald Trump.

@@

We built a Bayesian logistic regression model using the `stan_glm()` function of the `rstanarm` package [@rstanarm]. The model that we use is:

```{=tex}
\begin{align} 
\scriptsize
vote\_biden_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
\mbox{logit}(\pi_i) &= \beta_0 + \beta_1 \text{sex}_i + \beta_2  \text{age\_bracket}_i + \beta_3 \text{race}_i + \beta_4 \text{education\_level}_i + \beta_5 \text{state}_i + \beta_6  \text{urban}_i \\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
\beta_2 &\sim \mbox{Normal}(0, 2.5)
\end{align}
```
We run our model in R [@citeR] using the `stan_glm()` function of the `rstanarm` package [@rstanarm]. We use the default priors from `rstanarm`. We then applied our logistic regression model to the ACS Census data [@citeIPUMS].

@@

Concerns about our model are discussed in more detail in @sec-weaknesses-limitations.

@@

## Popular Vote Prediction

@@

Logistic regression is limited to the binary classification case, therefore using it l

@@

## Additional Data Details

@@

## Additional Tables

# biden_support_by_state <-
#   presidential_vote_model |>
#   add_epred_draws(newdata = props) |>
#   rename(support_biden_predict = .epred) |>
#   mutate(support_biden_predict_prop = support_biden_predict * prop) |>
#   ungroup() |>
#   summarise(support_biden_predict = sum(support_biden_predict_prop),
#             .by = c(state, .draw)) |>
#   summarise(
#     mean = mean(support_biden_predict),
#     lower = quantile(support_biden_predict, 0.025),
#     upper = quantile(support_biden_predict, 0.975),
#     .by = state
#   )

@@

### Model Summary

@@

### Coefficients

@@

### Posterior Predictive Check

@@

### Trace Plot and Rhat Plot

@@

### Credibility Intervals

In @fig-modelplot, we show the 90% credibility intervals for the predictors of `vote_biden`.
